---
title: "TPSC estimation experiments E1-E2 (supplement Appendix F)"
output: html_document
---

Stage-1 only: how $\Psi = (\tau, w, \sigma, \delta)$ is estimated and how well the estimate behaves.

These are the experiments reported in Appendix F of the supplement, "Numerical
implementation details". The four parameter configurations S1-S4 used throughout
are supplement Table F.1.

| lab code | what it is | manuscript |
|---|---|---|
| **E1a** | three estimators M0-M2 on common random numbers | Table F.2 (M0 = *Ours*, M1 = *Greedy*, M2 = *Simplex*) |
| **E1b** | sensitivity of the fit to the parameter box | Table F.3 |
| **E2a** | finite-sample properties of the MLE; convergence rates | Table F.4 |
| **E2b** | the delta-oracle contrast | Table F.5 |

```{r setup}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
source("R/00b_setup_lab.R")
```

## E1 - estimators and the parameter box

```{r E1}
E1 <- run_E1()
knitr::kable(E1$E1a, digits = 3, caption =
  "Table F.2 (per-configuration detail). Three estimators: M0 shipped = *Ours*,
   M1 near-global LHS = *Greedy*, M2 Nelder-Mead = *Simplex*, on common random
   numbers. The manuscript table averages these rows over S1-S4.")
knitr::kable(E1$E1b, digits = 4, caption =
  "Table F.3. Box sensitivity at the likelihood level (nll0, d_nll) and the
   distribution level (kl0, d_kl0). Read each level's median and q95
   separately: a box can leave the typical fit untouched while controlling the
   tail (the w bounds), or move the median outright (the delta ceiling).")
```

## E2 - finite-sample properties of the TPSC MLE

```{r E2}
E2 <- run_E2()
knitr::kable(E2$E2a, digits = 3, caption =
  "Table F.4 (input). Parameter recovery + density-level divergence, per
   (config, n); the log-log regressions below are fitted on these rows.")
knitr::kable(E2$table1_parameter_rate, digits = 3, caption =
  "Table F.4, parameter block. log(RMSE) on log(n) for (theta, w, sigma):
   slope ~ -1/2 is the parametric rate.")
knitr::kable(E2$table2_kl_rate, digits = 3, caption =
  "Table F.4, divergence block. log(median KL) on log(n): slope ~ -1 is the
   parametric rate.")
knitr::kable(E2$E2b, digits = 4, caption =
  "Table F.5 (per-n detail). Transform fidelity and the delta-oracle contrast. The benchmark
   for kl_oracle_ratio is median(chisq_4)/median(chisq_3) = 1.4187, i.e. the
   cost of one extra parameter.")
knitr::kable(E2$table3_oracle, digits = 4, caption =
  "Table F.5. One-point delta-oracle comparison at n = 1000. kl_oracle_ratio
   is contrasted against the 1.4187 benchmark.")
```

```{r session}
sessionInfo()
```
